Bandwidth-Aware Reconfigurable Memory Design with Hybrid Memory Technologies

### 2011-04-05 trunk/paper.tex

Figure~\ref{fig:hw-overview} shows an overview of BAROM hardware configuration.
The CMP platform consists of multiple cores, where L1 cahces are private to each
core and lower level caches are shared by the cores. With the provided bandwidth
vs. capacity curves of various memory technologies that are obtained using the
method described in section~\ref{sec:tech-explore}, we can design a hybrid
on-chip memory system to always provide the highest bandwith. In order to
achieve this goal, we configure the memory hierarchy in the following
manner.\vspace{5pt}

@@

\noindent{}{\bf{Memory technology of each level.}} The memory technology with
the highest provided bandwidth within the given range of capacity of each level
is selected. In our case, SRAM, STT-RAM, and RRAM are selected as the L2, L3, and
L4 caches respectively. As a result, the overall provided bandwidth curve of the
on-chip memory system will appear to be an envelope line of all the available
memory technologies as shown in Figure~\ref{fig:pbw-overall}.\vspace{5pt}

\noindent{}{\bf{Capacity of each level.}} The maximum availabe capacity of each
level is determined by the cross point of two memory technologies. In our case,
the capacities of SRAM/L2, STT-RAM/L2, and RRAM/L4 are 2MB, 512MB, and 1GB
respectively.\vspace{5pt}

When the system is initially powered on, the capacity of each level is defined
to be the maximum available capacity of the level.

>>>>

Figure~\ref{fig:hw-config} shows an overview of BAROM hardware configuration.
The CMP system consists of multiple cores, where L1 cahces are private to each
core and lower level caches are shared by the cores. With the provided bandwidth
vs. capacity curves of various memory technologies that are obtained using the
method described in section~\ref{sec:tech-explore}, we can design a hybrid
on-chip memory system to always provide the highest bandwith. In order to
achieve this goal, we configure the memory hierarchy in the following
manner.\vspace{5pt}

@@

\noindent{}{\bf{Memory technology of each level.}} The memory technology with
the highest provided bandwidth within the given range of capacity of each level
is selected. In our case, SRAM, STT-RAM, and RRAM are selected as the L2, L3,
and L4 caches respectively. As a result, the overall provided bandwidth curve of
the on-chip memory system will appear to be an envelope line of all the
available memory technologies as shown in
Figure~\ref{fig:pbw-envelope}.\vspace{5pt}

\noindent{}{\bf{Capacity of each level.}} The maximum availabe capacity of each
level is determined by the cross point of two memory technologies. In our case,
the capacities of SRAM/L2, STT-RAM/L2, and RRAM/L4 are 2MB, 512MB, and 1GB
respectively. At the system initialization, the capacity of each level is
defined to be the maximum available capacity of the level. According to the
reqirement of different applications, the capacities can be reconfigured at
run-time to provide best performance. The memory space of each level can also be
reconfigured to form an internal level as shown in Figure~\ref{fig:hw-config}.
The hardware and software supports for reconfiguration will be presented in the
following sections.

When the system is initially powered on,
